Preprocessing

### 2023-08-14 docs/presentation/preprocess.Rmd
viz: select used cols

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

q8 <- append(q8_q3, q8_q4)
q8$Everyone <- q8_to_likert()
saveRDS(q8, file = "data/q8.rds")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")
```

>>>>

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

q8 <- append(q8_q3, q8_q4)
q8$Everyone <- q8_to_likert()
# saveRDS(q8, file = "data/q8.rds")
```

## Save
```{r}
analysis %>%
  select(
    Q3_recoded, Q4, Q5,
    dat_rec, pro_rec, res_rec, con_rec, label,
    starts_with("Q7"),
    Q13_1, Q13_2,
    starts_with("Q9"),
    starts_with("Q14"),
    starts_with("Q17_")
  ) %>%
  saveRDS("data/analysis.rds")
```
